Naming Anonymous JavaScript Functions

### 2011-04-14 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
final changes to avoid splitting code

\begin{abstract}
JavaScript developers create and call functions; they use functions to construct objects. JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and object representations. However, developers need not to specify names for functions.  
 Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
By studying examples from these JavaScript projects, we propose \textit{Static Function-Object Consumption}, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions. We applied our approach to 90000 anonymous functions appeared in the analyzed JavaScript project. The approach is successful in naming more than 99\% (91\% are unique in file) of anonymous functions while the average length of function names is kept less than 37 characters.% which is appropriate for presentation.

@@

\section{Introduction}
The unique and important role of JavaScript in web programming is undeniable. Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site. This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}\cite{Richards1}. It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards2}. There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.

To cope with these large and sophisticated systems, JavaScript developers turn to better development tools. These tools analyze then represent the program in ways that the developer might only be able to imagine through substantial time-consuming reading of source code.  One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack.

All of these tools need to express program artifacts in a compact way the developer can understand.  For example, the debugger needs to present the execution call stack so the developer can understand which functions are currently active.  Obviously a particularly good compact representation would be a name given by the developer in the source code. However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones. Anonymous artifacts prevent tools from communicating effectively with developers.

Among program artifacts, functions are central to program comprehension in JavaScript. In addition to their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call. However, functions can be defined and created without a name or identifier.

In this paper, we analyze ten large, well-known projects. We show that within these projects less than 7\% of the function bodies are named. 
We analyze the syntactic constructs that function bodies appear in and rationalize how developers think about the bodies in relation to the structure of the code.
We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.

@@

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects\footnote[2]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}. For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}. The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent. Among all functions only a very limited number of them (116 functions) are defined by the \verb|Function| constructor. Our analysis does not include the functions defined dynamically by \verb|eval| function or \verb|new Function()|; these cases would only make the ratio even smaller.  Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

To understand the consequences of anonymous functions on development tools we will focus on one example, the impact on debuggers.
Two main issues appear in debuggers due to the lack of function name. First, object constructor name, which can facilitate understanding the object value, is not available in the object summary. Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative. We discuss these issues in the next two subsections.

\subsection{Missed Constructor Name in Object Summary}
JavaScript does not support classes, but objects can be created by constructors (\verb|new| followed by a function call). A constructor is a regular JavaScript function. Once the \verb|new| keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to \verb|this| and the constructor is called. The role of constructor is to initialize the empty object. Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards2}, the constructor can still be useful in classifying the object.
Debuggers employ this fact and display the constructor name in the object summary to facilitate the developer's understanding.

@@

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.png}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.png}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|. However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| as their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify both objects in the general \verb|Object| class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. \verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or in some cases infer misleading names.

\subsection{Anonymous Function Names in Call-stack View}
The second problem is the call-stack.
To illustrate this, we pause the program (Figure~\ref{js-code}) at line 12 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Among three last functions in the call stack, Google Chrome only shows the name of first function (\verb|main|) correctly. For the second function (line 22), it shows \verb|anonymous|, and for the last function (line 12), it gives a wrong name, \verb|foo|. Firebug performs better by guessing two function names correctly, but it still fails in one case. It shows \verb|main| as the name of last function(line 12) which is the name of another function (the enclosing function at line 9). In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.png}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.png}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

@@

\subsection{What Makes a Good Function Name?}
A function name is basically used to assist the developer to recall or understand the function behavior. For a developer who is already familiar with the function, it works more like an identifier. However, this identifier should be easily recognized by the developer. For example, a naive proposal for the function name is a combination of the function file name and its first line number. Although it may work as an identifier, but it does not assist the developer to recall or understand the function behavior.

 On the other hand, for a developer who does not know the function, a function name should explains the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}). A function name must not be too long that can not be displayed or read by the developer. For example, the function body explains the function behavior well however it is not an appropriate function name.

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packaging mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate objects, properties and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.

\section{Building Up Intuition by Example}
\label{sec:intuition}
We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions. We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.  To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions. We want to see what kinds of cases are important and what aspects of these cases help us identify functions.

For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.  Then we examine each of these cases to think about how we want the functions named. We will ignore nesting of function scopes in the analysis to avoid taking on too much at one time.

@@

@@

Following the model from Case 1, we expect a good name would combine the object name with the property identifier. The complication in this case comes from the object name: in general the object reference can be a computed expression \footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}. Here is a simple example from the Closure project: 
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  this.eventPool_.createObject = function() {
    return new goog.debug.Trace_.Event_();
  };
\end{lstlisting}

 These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small. For example, \verb|this.| add no information to the name since we cannot know the value of \verb|this| while parsing.

\subsection{Case 4: Property Assignment With  Property Name String}
In JavaScript, objects are like hashmaps and their properties can also be accessed by a string can be specified in the brackets after the object. Semantically this is the same as the previous case and we see few instances of this form for function object assignment. The string inside the brackets can be considered a property identifier for naming.

@@

If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use). In this case we cannot use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name. To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.

@@

We will describe the details in the next sections. In constructing names we realized one additional aspect: as we move from simple object property names to more complex examples, the path of the object consumption is an added bit of information helpful in naming. Thus we add some symbols to guide the developer to the function body in complex cases: this way the extra information does not take a lot of space and it can be ignored by developers who have not yet learned about its significance.

@@

In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. We reduce these expressions to pseudo-identifiers (i.e. not necessarily a valid JavaScript identifier) that resembles the expression. This work is done during the Object Consumption Summary algorithm in the functions described here:
\paragraph{Identifiers for Function Arguments} Search for all literal string nodes in other arguments and concatenated them by ``-'', dropping  characters over 10.  
 (This work is on in Algorithm~\ref{alg1} in \verb|argSummary|).
\paragraph{Identifiers for Assignments and Function calls} This function gets called for nodes resulting from the last 2 rows of Table~\ref{table:node-types}. The expressions here will evaluate to a writable or readable address, so we want to extract the most specific developer-invented identifiers from the expression. Thus we apply the rules from Table~\ref{expression-reduction}, which starts from the right hand side of the expression; we skip any JavaScript keywords like \texttt{this} or \texttt{prototype}. We also skip any pattern which does not match (e.g., a function call). (This work is on in Algorithm~\ref{alg1} in \verb|nameExpressions|.)

Obviously these rules are heuristic and can be improved through experience and interaction with developers. We are attempting to balance information content with length. Large complex expressions will give pseudo-identifiers which are complex, but with some identifiable parts.

@@

The third function on line 18 is called immediately after definition, on line 24. This means the function body in the syntax tree will have a parent from the immediate call then the assignment; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|. The name becomes \verb|FOO<|.

@@

In Table~\ref{evaluation} We compared our results to Firebug's naming output for each of the 10 projects used previously and listed in Appendix 1. Firebug does not use a parser for naming functions. It instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name (a function called {\small \texttt{guessFunctionName()}}). Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases. About 10 percent (the second column) of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm). The third column shows that only FOC-Locall name more than 98 percent of anonymous functions. By adding the enclosing function names, this number increases to more than 99 percent for FOC-Full(the fourth column). Based on our observations, most functions remain anonymous in FOC-Full are top level \textit{immediate} functions which are usually used for creating a local scope for a set of variables.

The duplicates columns show the number of functions which get a name which is also assigned to another function(s) for Firebug, FOC-Local and FOC-FULL. The number shows that Firebug assigns duplicate names to about 47 percent of anonymous functions. The first reason behind this huge number is that Firebug relies on regular expressions instead of abstract syntax tree for locating names. The second reason is that Firebug does not analyze the function object flow but tries to construct the name from the identifiers close to function definition. The second column shows that FOC-Local gives much less duplicates (13\%) comparing to Firebug. It means that local names with are sufficient for recognizing function while they have shorter length than full names. The third column says that less than 9 percent of anonymous functions get duplicated names by full names. Based on our observations, many of duplicates in projects such as DOJO, ExtJS and YUI come from test files. In a test file the same use case is repeated with different data and therefore the same function names appear several times. In projects like JQuery, Prototype, MooTools the conditional statements are the main source of duplicates. These libraries usually check against different environment properties (e.g., browser) to load the appropriate function.

@@

\begin{table*}[htp]
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l |}
  \hline
\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Duplicates by}              & \multicolumn{3}{|c|}{Local/Full Length}  \\ 
  \cline{2-11}
                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    Firebug          &    FOC-Local   & FOC-Full    & Average   & Longest & \textgreater50/\textgreater80 \\ 
  \hline 
   Closure       & 8987      &   312(3\%)     & 51        & 10        &    662(7\%)         &    211(2\%)    & 103(1\%)    & 33/35      & 76/101 & 471/30  \\ 
  \hline 
   DoJo          & 15866     &   3362(21\%)   & 528       & 390       &    3325(21\%)       &    2993(19\%)  & 2287(14\%)  & 24/36      & 81/162 & 680/765 \\ 
  \hline 
   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    23777(65\%)      &    3737(10\%   & 2342(7\%)   & 22/25      & 65/91  & 177/2 \\ 
  \hline 
   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    481(16\%)        &    85(3\%)     & 32(1\%)     & 27/36      & 70/140 & 76/18 \\ 
  \hline  
   jQuery        & 399       &   95(24\%)     & 9         & 8         &    162(40\%)        &    97(24\%)    & 56(14\%)    & 14/18      & 50/65  & 0/0 \\ 
  \hline  
   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    491(27\%)        &    314(17\%)   & 191(10\%)   & 17/22      & 49/80  & 0/0 \\ 
  \hline 
   MooTools      & 618       &   121(19\%)    & 30        & 18        &    272(44\%)        &    158(26\%)   & 138(22\%)   & 12/14      & 36/73  & 0/0 \\ 
  \hline 
   Prototype     & 442       &   125(28\%)    & 24        & 19        &    154(35\%)        &    70(16\%)    & 70(16\%)    & 21/25      & 55/88  & 5/1 \\ 
  \hline  
   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    306(36\%)        &    131(19\%)   & 86(9\%)     & 21/27      & 55/132 & 7/5  \\ 
  \hline    
   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    10073(47\%)      &    3558(17\%)  & 2205(10\%)  & 16/37      & 114/145 & 223/292 \\ 
  \hline 
   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    39703(44\%)      &    11354(13\%) & 7510(8\%)   & N/A       & N/A      & 1639/1113 (3\%)  \\ 
  \hline       
  \end{tabular}
  }
\caption{Results of Function Object Consumption. The rows are the projects listed in Appendix 1. First column contains the number of anonymous functions in each project. The second column shows the number of functions Firebug could not name. The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm; and the fourth column is the number with only a name for enclosing scopes. The next three column gives the number of times a Firebug, FOC-Local and FOC-Full function name appears twice in a file. The last three columns contain the length information. Every cell has two entries divided by a slash, the first is the local name and the second is the full name. The eighth and ninth columns give the average and longest name character counts respectively. The last columns shows the number of functions get local names/full names with length greater than 50/80 characters.} 
 \label{evaluation} 
\end{table*}

>>>>

\begin{abstract}
JavaScript developers create programs by calling functions and they use functions to construct objects. JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and in object representations. However, most functions are anonymous: developers need not to specify names for functions.  
 Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
After studying examples from these JavaScript projects, we propose \textit{Static Function-Object Consumption}, a principled, automated approach based on local source code analysis for providing names to nameless JavaScript functions. We applied our approach to 90000 anonymous functions that appeared in the analyzed JavaScript project. The approach is successful in naming more than 99\% (91\% are unique within their file) of anonymous functions while the average length of function names is kept less than 37 characters.% which is appropriate for presentation.

@@

\section{Introduction}
The unique and important role of JavaScript in web programming is undeniable. Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site. This language is used by the Web's 100 most popular sites\footnote[1]{http://www.alexa.com}\cite{Richards1}. It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Moreover, JavaScript is also becoming a general purpose computing platform\cite{Richards2} for office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and even program development environments \cite{Ingalls}. There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.

To cope with these large and sophisticated systems, JavaScript developers turn to development tools. One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack.

All of these tools need to express program artifacts in a compact way the developer can understand.  For example, the debugger must present the execution call stack so the developer can understand which functions are currently active.  Obviously a particularly good compact representation would be a name given by the developer in the source code. However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones. Anonymous artifacts prevent tools from communicating effectively with developers.

Among program artifacts, functions are central to understanding a JavaScript program. In addition to their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.  These functions can be defined and created without a name or identifier.

In this paper, we analyze ten large, well-known projects. We show that within these projects less than 7\% of the function bodies are named. 
We analyze the syntactic constructs surrounding these function bodies and rationalize how developers think about the bodies in relation to the structure of the code.

We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and call-stack views, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.

@@

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects\footnote[2]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}. For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}. The average ratio of named functions to all functions is less then 7 percent and, excepting one project, \textit{Prototype}, the ratio does not exceed 13 percent. Among all functions only a very limited number of them (116 functions) are defined by the \verb|Function| constructor. Our analysis does not include the functions defined dynamically by \verb|eval| function or \verb|new Function()|; these cases would only make the ratio even smaller.  Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

To understand the consequences of anonymous functions on development tools we will focus on one example, the impact on debuggers.
Two main issues appear in debuggers due to the lack of function name. First, the object constructor name, which can facilitate understanding the object value, is not available in the object summary. Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative. We discuss these issues in the next two subsections.

\subsection{Missed Constructor Name in Object Summary}
\label{sec:missedctor}
JavaScript does not support classes, but objects can be created by constructors (\verb|new| followed by a function call). A constructor is a regular JavaScript function. Once the \verb|new| keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to \verb|this| and the constructor is called. The role of constructor is to initialize the empty object. Unlike class-based object-oriented languages, the structure of the object  may change during the object's lifetime \cite{Richards2}. Nevertheless, the constructor can still be useful in classifying the object most of the time.
Debuggers employ this fact and display the constructor name in the object summary to facilitate the developer's understanding.

@@

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.png}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.png}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}. The content of these views is discussed in Sec.~\ref{sec:missedctor} }
\label{debuggers-objects}
\end{figure*}

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|.

The Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| in their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences.

Firebug classifies both objects in the general \verb|Object| class, but includes some of the object properties in the summary. These additional properties may give a hint to the developer about the object structures. \verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior: the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or they infer a misleading name.

\subsection{Anonymous Function Names in Call-stack View}
\label{sec:callstack}
The second problem is the call-stack.
To illustrate this, we pause the program (Figure~\ref{js-code}) at line 12 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Among the three top functions in the call stack, Google Chrome shows only the name of the third one down, function (\verb|main|), correctly. For the second frame from the top (marked as line 22), it shows \verb|anonymous|, and for the top frame (marked at line 12), it gives a wrong name, \verb|foo|. Firebug performs better by guessing two function names correctly, but it still fails in one case. It shows \verb|main| as the name of the function on the top frame (marked at line 12) but this is the name of another function (the enclosing function at line 9). In these cases, the information provided by the debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.png}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.png}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}. The contents of these views are discussed in Sec.~\ref{sec:callstack} }
\label{debuggers-callstack}
\end{figure*}

@@

\subsection{What Makes a Good Function Name?}
A function name is basically used to assist the developer to recall or understand the function behavior. For a developer who is already familiar with the function, it works more like an identifier. However, this identifier should be easily recognized by the developer. For example, a naive proposal for the function name is a combination of the function file name and its first line number. Although it may work as an identifier, it does not assist the developer to recall or understand the function behavior.

 On the other hand, for a developer who does not know the function, a function name should explain the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}). A function name must not be so long that it can not be displayed or read by the developer. For example, the entire function body source code explains the function behavior well, however it is not an appropriate function name.

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packaging mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate objects, properties and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module that contains the function. In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.

@@

\section{Building Up Intuition by Example}
\label{sec:intuition}
We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions. We have to create salient information from source code: we anticipate that removing characters will be our biggest challenge.  To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions. We want to see what kinds of cases are important and what aspects of these cases help us identify functions.

For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of these 12 cases, giving the numerical results in Table~\ref{function-type-count}.  Then we examine each of these cases to think about how we want the functions named. We will skip over the nesting of function scopes in the analysis to avoid taking on too much at one time; we return to this aspect at the end of this section.

@@

Following the model from Case 1, we think a good name would combine the object name with the property identifier. The complication in this case comes from the object name: in general the object reference can be a computed expression\footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}. Here is a simple example from the Closure project: 
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  this.eventPool_.createObject = function() {
    return new goog.debug.Trace_.Event_();
  };
\end{lstlisting}

In general, the expression can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small. For example, \verb|this.| add no information to the name since we cannot know the value of \verb|this| while parsing.

\subsection{Case 4: Property Assignment With  Property Name String}
In JavaScript, objects are like hashmaps and their properties can also be accessed by a string  specified in the brackets after the object. Semantically this is the same as the previous case and we see few instances of this form of function object assignment. The string inside the brackets can be considered a property identifier for naming.

@@

If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use). In this case we cannot use the assignment target idea from Case 1, but the source proximity and the developer-invented names concepts point to using interior identifiers in a name. To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create in this way is for an immediately called function.

@@

We will describe the details in the next sections. In constructing names we realized one additional aspect: as we move from simple object property names to more complex examples, the path of the object consumption is an added bit of information helpful in naming. Thus we add some symbols to guide the developer to the function body in complex cases: in this way the extra information does not take a lot of space and it can be ignored by developers who have not yet learned about its significance. We describe these symbols in Sec.~\ref{sec:concatenation}.

@@

In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will be written in place of an identifier. We reduce these expressions to pseudo-identifiers (i.e. not necessarily a valid JavaScript identifier) that resembles the expression. This work is done during the Object Consumption Summary algorithm in the functions described here:
\paragraph{Identifiers for Function Arguments} Search for all literal string nodes in other arguments and concatenated them by ``-'', dropping  characters beyond 10.  
 (This work is on in Algorithm~\ref{alg1} in \verb|argSummary|).
\paragraph{Identifiers for Assignments and Function calls} This function gets called for nodes resulting from the last 2 rows of Table~\ref{table:node-types}. The expressions here will evaluate to a writable or readable address, so we want to extract the most specific developer-invented identifiers from the expression. Thus we apply the rules from Table~\ref{expression-reduction}, which starts from the right hand side of the expression; we skip any JavaScript keywords like \texttt{this} or \texttt{prototype}. We also skip any pattern which does not match (e.g., a function call). (This work is on in Algorithm~\ref{alg1} in \verb|nameExpressions|.)

Obviously these rules are heuristic and can be improved through experience and interaction with developers. We are attempting to balance information content with length. Large complex expressions will give pseudo-identifiers which are complex, but with some identifiable parts adequate for developer recognition and search.

@@

The third function on line 18 is called immediately after definition, on line 24. This means the function body in the syntax tree will have a parent from the immediate call and then the assignment parent node; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|. The name becomes \verb|Foo<|.

@@

In Table~\ref{evaluation} we compared our results to Firebug's naming output for each of the 10 projects used previously and listed in Appendix 1. Firebug does not use a parser for naming functions. It instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name (a function called {\small \texttt{guessFunctionName()}}). Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases. About 10 percent (the second column) of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm). The third column shows that more than 98 percent of anonymous functions have a FOC-defined local name. By adding the enclosing function names, this number increases to more than 99 percent for FOC-Full(the fourth column). Based on our observations, most functions remaining anonymous in FOC-Full are top level \textit{immediate} functions which are usually used for creating a local scope for a set of variables.

The "Duplicates By" columns show the number of functions which get a name which is also assigned to another function(s) for Firebug, FOC-Local and FOC-Full. The number shows that Firebug assigns duplicate names to about 47 percent of anonymous functions. The first reason behind this huge number is that Firebug relies on regular expressions instead of abstract syntax tree for locating names. The second reason is that Firebug does not analyze the function object flow but tries to construct the name from the identifiers close to function definition. The second column shows that FOC-Local gives much less duplicates (13\%) comparing to Firebug. This means that local names are sufficient for recognizing functions within a file, which is helpful because they have shorter length than full names. The third column says that less than 9 percent of anonymous functions get duplicated names by full names. Based on our observations, many of duplicates in projects such as DOJO, ExtJS and YUI come from test files. In a test file the same use case is repeated with different data and therefore the same function names appear several times. In projects like JQuery, Prototype, MooTools the conditional statements are the main source of duplicates. These libraries usually check against different environment properties (e.g., browser) to load the appropriate function.

@@

\begin{table*}[htp]
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l |}
  \hline
\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Duplicates by}              & \multicolumn{3}{|c|}{Local/Full Length}  \\ 
  \cline{2-11}
                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    Firebug          &    FOC-Local   & FOC-Full    & Average   & Longest & \textgreater50/\textgreater80 \\ 
  \hline 
   Closure       & 8987      &   312(3\%)     & 51        & 10        &    662(7\%)         &    211(2\%)    & 103(1\%)    & 33/35      & 76/101 & 471/30  \\ 
  \hline 
   DoJo          & 15866     &   3362(21\%)   & 528       & 390       &    3325(21\%)       &    2993(19\%)  & 2287(14\%)  & 24/36      & 81/162 & 680/765 \\ 
  \hline 
   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    23777(65\%)      &    3737(10\%   & 2342(7\%)   & 22/25      & 65/91  & 177/2 \\ 
  \hline 
   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    481(16\%)        &    85(3\%)     & 32(1\%)     & 27/36      & 70/140 & 76/18 \\ 
  \hline  
   jQuery        & 399       &   95(24\%)     & 9         & 8         &    162(40\%)        &    97(24\%)    & 56(14\%)    & 14/18      & 50/65  & 0/0 \\ 
  \hline  
   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    491(27\%)        &    314(17\%)   & 191(10\%)   & 17/22      & 49/80  & 0/0 \\ 
  \hline 
   MooTools      & 618       &   121(19\%)    & 30        & 18        &    272(44\%)        &    158(26\%)   & 138(22\%)   & 12/14      & 36/73  & 0/0 \\ 
  \hline 
   Prototype     & 442       &   125(28\%)    & 24        & 19        &    154(35\%)        &    70(16\%)    & 70(16\%)    & 21/25      & 55/88  & 5/1 \\ 
  \hline  
   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    306(36\%)        &    131(19\%)   & 86(9\%)     & 21/27      & 55/132 & 7/5  \\ 
  \hline    
   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    10073(47\%)      &    3558(17\%)  & 2205(10\%)  & 16/37      & 114/145 & 223/292 \\ 
  \hline 
   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    39703(44\%)      &    11354(13\%) & 7510(8\%)   & N/A       & N/A      & 1639/1113 (3\%)  \\ 
  \hline       
  \end{tabular}
  }
\caption{Results of Function Object Consumption. The rows are the projects listed in Appendix 1. The first column contains the number of anonymous functions in each project. The second column shows the number of functions Firebug could not name. The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm; and the fourth column is the number of functions the FOC leaves without a name even from enclosing scopes. The next three columns give the number of times a Firebug, FOC-Local, and FOC-Full function name appears twice in a file, respectively. The last three columns contain the length information. Every cell has two entries divided by a slash, the first is the local name and the second is the full name. The eighth and ninth columns give the average and longest name character counts respectively. The last columns shows the number of functions with local names greater then 50 characters in length separated by a slash from the number of functions wit full names with length greater than 80 characters.} 
 \label{evaluation} 
\end{table*}
